\chapter{Introduction}
\label{chap:intro}

Modern Infrastructure as a Service (IaaS) providers rely on various network protocols to provide efficient service management abilities. These protocols, as well, rely heavily on the ability to provide correct and efficient network monitoring that generates the needed statistics. Such protocols belong to various service management sub-domains such as traffic engineering~\cite{microte}, anomaly detection~\cite{Moraney2016}, load balancing~\cite{networkLB}, NFV placements~\cite{NFV-dor} and many more.

The ability to provide accurate per flow statistics, while greatly important for service management protocols, is often impractical due to the high number of active flows and the limited on-chip memory needed to keep such counters. Furthermore, no remediation is expected in the near future; more flows are flowing through networks than before, the line rate is ever increasing requiring counters with more width and more monitoring applications are running, requiring their own portion of the available memory. 

Given these limitations, it is important to consider designing and implementing efficient practical algorithms for various monitoring tasks. We consider an algorithm to be an efficient practical monitoring algorithm if (1) it provides important monitoring data, (2) performs $O(1)$ operations per packet to cope with line rate, (3) uses a constant limited amount of memory that is much smaller than and not related to the number of active flows, and finally (4) implementable on memory schemes of off-the-shelf network gear.

The problems of detecting the top-$k$ flows, the heavy hitter flows, and the hierarchical heavy hitter flows, are typical monitoring tasks in the sense that they are straightforward to solve with memory-intensive solutions. When sufficient memory is available, one can track the frequency of each flow and process the frequencies off-line to detect the required flows. However, with memory constraints in mind, it is challenging to design monitoring algorithms for these problems using constant (or even sub-linear) space with respect to the number of active flows or the overall traffic size.

Many of the current state-of-the-art and most notable monitoring schemes require a non-constant amount of memory depending either on the traces size or in inverse relation to the guaranteed accuracy~\cite{slidingHH,metwally2005efficient,SpaceSaving,Ben-Basat2017}. In such schemes, the required memory is usually of size $o(\frac{1}{\epsilon})$ where $\epsilon$ is the guaranteed accuracy. This notation hides the fact that in many practical use-cases their memory requirement is higher than what is available in the network device.

With the increasing amount of various monitoring applications running concurrently on network devices, the approach of setting accuracy parameters per application and only then count for their required memory is not operational. This approach makes it hard for network operators to meet the memory constraint by prioritizing applications and optimizing their accuracy parameters. The correct approach to manage on-device monitoring applications is to set hard constraints on their memory footprint and only then set the desired accuracy parameters while slightly compromise the quality of the monitoring results according to the available resources. 

The quality of the monitoring results is commonly measured via two metrics, \textit{Recall} and \textit{False Positive Rate} (FPR). Recall (sometimes referred to also as Detection Rate) measures the proportion of positives items that are correctly identified while the FPR measures the proportion of the none-positive items that are reported as positive (i.e. misidentified) from the set of reported items.  Describing the quality of the monitoring data without reporting both metrics is not complete. Since, while high recall algorithms are preferred, this should not come at a price of a very high FPR. An extreme example of such an algorithm is the one that reports all flows as positive, this algorithm will have a recall of $100\%$ but also almost a $100\%$ FPR hindering its output useless.

Having on-device monitoring algorithms that support line rate is of high importance, no network operator in the right mind would consider reducing network capacity due to the deployment of monitoring algorithms on devices. The guarantee of line rate performance usually manifests in having $O(1)$ operations per packet, the motivation is if the algorithm performs only ``lightweight" operation per arriving packet it would meet the line rate requirement.

Many monitoring algorithms maintain complex schemes and data structures that require once in a while perform a ``heavy" operation (for example a re-ordering of the data scheme). Algorithms of this type claim to support line rate while having an amortized $O(1)$ operation by proving that this ``heavy" operation happens once in many packets and when its cost is split among all the relevant packets it would add a constant negligible effect.

This point of view on line rate operation is in many cases impractical. While truly it is an amortized $O(1)$ operation, during such operations, arriving packets must be stored to be later processed and this could affect the device's available buffers and affects its performance. Thus, one of our motivations is to design a scheme that performs worst-case $O(1)$ operation.

The rest of the dissertation is organized as follows; In Chapter~\ref{cha:topk} we introduce the top-$k$ problem and our efficient practical algorithms that outperform the state of the art algorithms for the weighted variant of the problem. In Chapter~\ref{cha:HHH} we follow the techniques of time-based reconfigurations of counters presented in Chapter~\ref{cha:topk}, to tackle the Hierarchical Heavy Hitter problem and introduce practical algorithms for it that match the state of the art algorithms while keeping with line rate and not requiring convergence period. In Chapter~\ref{cha:HH}, we present an algorithm based on shared estimators for the Heavy Hitter problem that outperforms the state of the art algorithm for amounts of memory less than 0.25MB. Finally, we conclude in Chapter~\ref{chap:conclusion}.

